FCST

### 2021-03-05 analysis/chapters/forecast_20181122.Rmd
Campos de variables

  geom_line(alpha = 0.1, 
            aes(y = BIAS, color = exp, group = interaction(exp, mem))) +
  geom_line(aes(color = exp, linetype = estadistico)) +
  geom_hline(yintercept = 0, color = "grey30") +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  coord_flip() +
  facet_grid(fcst_exp + iop~variable, scales = "free_x", 
             labeller = labeller(variable = c("t" = "Temperature",
                                              "td" = "Dew point\ntemperature",
                                              "u" = "U wind",
                                              "v" = "V wind"))) +
  labs(y = NULL, x = "Height (Km)", color = NULL, linetype = NULL) +
  theme_minimal() geom_hline(yintercept = 0, color = "grey30") +
```

@@

obs_ens_00 <- read_rds(paste0(derived_data, "/interp_obs/interp_obs_2018112200_mem.rds"))
obs_ens_06 <- read_rds(paste0(derived_data, "/interp_obs/interp_obs_2018112206_mem.rds"))

rbind(obs_00, obs_06) %>% 
  .[usage.flag == 1] %>% 
  .[, .(rmse = sqrt(mean((obs - fcst)^2, na.rm = TRUE)),
        bias = mean(obs -  fcst, na.rm = TRUE)), by = .(var, date, exp, fcst_exp)] %>% 
  melt(measure.vars = c("rmse", "bias"), variable.name = "estadistico") %>% 
  .[estadistico == "rmse"] %>% 
  ggplot(aes(date, value)) +
  geom_line(aes(color = exp, linetype = fcst_exp)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  scale_date() +
  labs(subtitle = "RMSE", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_wrap(~ var, scales = "free_y") +
  theme_minimal()

rbind(obs_00, obs_06) %>% 
  .[usage.flag == 1] %>% 
  .[, .(rmse = sqrt(mean((obs - fcst)^2, na.rm = TRUE)),
        bias = mean(obs -  fcst, na.rm = TRUE)), by = .(var, date, exp, fcst_exp)] %>% 
  melt(measure.vars = c("rmse", "bias"), variable.name = "estadistico") %>% 
  .[estadistico == "bias"] %>% 
  ggplot(aes(date, value)) +
  geom_hline(yintercept = 0, color = "grey60") +
  geom_line(aes(color = exp, linetype = fcst_exp)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  scale_date() +
  labs(subtitle = "BIAS", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_wrap(~ var, scales = "free_y") +
  theme_minimal()
```

@@

extremos <- rbind(obs_ens_00, obs_ens_06) %>% 
  .[, .(max_rmse = max(RMSE),
        min_rmse = min(RMSE)), by = .(var, exp, fcst_exp, date)]

miembros <- rbind(obs_ens_00, obs_ens_06)

rbind(obs_00, obs_06) %>% 
  .[usage.flag == 1] %>% 
  .[, .(rmse = sqrt(mean((obs - fcst)^2, na.rm = TRUE)),
        bias = mean(obs -  fcst, na.rm = TRUE)), by = .(var, date, exp, fcst_exp)] %>% 
  melt(measure.vars = c("rmse", "bias"), variable.name = "estadistico") %>% 
  .[estadistico == "rmse"] %>% 
  extremos[., on = .NATURAL] %>% 
  ggplot(aes(date, value)) +
  geom_ribbon(aes(ymin = min_rmse, 
                  ymax = max_rmse, fill = exp), alpha = 0.2) +
  scale_fill_manual(guide = NULL, values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                                   E6 = "SATWND", E7 = "RAD")) +
  geom_line(aes(color = exp, linetype = fcst_exp)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  scale_date() +
  labs(subtitle = "RMSE", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_wrap(~ var, scales = "free_y") +
  theme_minimal()

rbind(obs_00, obs_06) %>% 
  .[usage.flag == 1] %>% 
  .[, .(rmse = sqrt(mean((obs - fcst)^2, na.rm = TRUE)),
        bias = mean(obs -  fcst, na.rm = TRUE)), by = .(var, date, exp, fcst_exp)] %>% 
  melt(measure.vars = c("rmse", "bias"), variable.name = "estadistico") %>% 
  .[estadistico == "rmse"] %>% 
  miembros[., on = .NATURAL] %>% 
  ggplot(aes(date, value)) +
  geom_line(alpha = 0.1, 
            aes(y = RMSE, color = exp, linetype = fcst_exp, group = interaction(exp, mem, fcst_exp))) +
  geom_line(aes(color = exp, linetype = fcst_exp)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  scale_date() +
  labs(subtitle = "RMSE", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_wrap(~ var, scales = "free_y") +
  theme_minimal()

@@

```{r}
miembros %>% 
  .[, mean_RMSE := mean(RMSE), by =  .(exp, fcst_exp, date, var)] %>% 
  ggplot(aes(date, RMSE)) +
  geom_line(aes(color = exp, linetype = fcst_exp, 
                grup = interaction(exp, fcst_exp, mem)), alpha = 0.1) +
  geom_line(aes(y = mean_RMSE, color = exp, linetype = fcst_exp)) +
   scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  scale_date() +
  labs(subtitle = "RMSE", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_wrap(~ var, scales = "free_y") +
  theme_minimal()
```

@@

>>>>

  geom_line(alpha = 0.1, 
            aes(y = BIAS, color = exp, group = interaction(exp, mem))) +
  geom_line(aes(color = exp, linetype = estadistico)) +
  geom_hline(yintercept = 0, color = "grey30") +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  coord_flip() +
  facet_grid(fcst_exp + iop~variable, scales = "free_x", 
             labeller = labeller(variable = c("t" = "Temperature",
                                              "td" = "Dew point\ntemperature",
                                              "u" = "U wind",
                                              "v" = "V wind"))) +
  labs(y = NULL, x = "Height (Km)", color = NULL, linetype = NULL) +
  theme_minimal() 
```

@@

media <- rbind(read_rds(paste0(derived_data, "/interp_obs/interp_obs_2018112200_mean2.rds")),
               read_rds(paste0(derived_data, "/interp_obs/interp_obs_2018112206_mean2.rds")))

miembros <- rbind(read_rds(paste0(derived_data, "/interp_obs/interp_obs_2018112200_mem.rds")),
                  read_rds(paste0(derived_data, "/interp_obs/interp_obs_2018112206_mem.rds")))

media %>% 
  melt(measure.vars = c("RMSE", "BIAS"), variable.name = "estadistico") %>% 
  .[estadistico == "RMSE"] %>% 
  ggplot(aes(date, value)) +
  geom_line(aes(color = exp, linetype = fcst_exp)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  scale_date() +
  labs(subtitle = "RMSE", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_wrap(~ var, scales = "free_y") +
  theme_minimal()

media %>% 
  melt(measure.vars = c("RMSE", "BIAS"), variable.name = "estadistico") %>% 
  .[estadistico == "BIAS"] %>% 
  ggplot(aes(date, value)) +
  geom_hline(yintercept = 0, color = "grey60") +
  geom_line(aes(color = exp, linetype = fcst_exp)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  scale_date() +
  labs(subtitle = "BIAS", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_wrap(~ var, scales = "free_y") +
  theme_minimal()
```

@@

extremos <- miembros %>% 
  .[, .(max_rmse = max(RMSE),
        min_rmse = min(RMSE)), by = .(var, exp, fcst_exp, date)]

media %>% 
  extremos[., on = .NATURAL] %>% 
  .[exp == "E7"] %>% 
  ggplot(aes(date, RMSE)) +
  geom_ribbon(aes(ymin = min_rmse, 
                  ymax = max_rmse, fill = exp, group = interaction(exp, fcst_exp)), alpha = 0.2) +
  scale_fill_manual(guide = NULL, values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                                   E6 = "SATWND", E7 = "RAD")) +
  geom_line(aes(color = exp, linetype = fcst_exp)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  scale_date() +
  labs(subtitle = "RMSE", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_wrap(~ var, scales = "free_y") +
  theme_minimal()

media %>% 
  .[, mem := "000"] %>% 
  rbind(., miembros) %>% 
  .[exp == "E7"] %>% 
  ggplot(aes(date, RMSE)) +
  geom_line(data = ~.x[mem != "000"], alpha = 0.1, 
            aes(y = RMSE, color = exp, linetype = fcst_exp, group = interaction(exp, mem, fcst_exp))) +
  geom_line(data = ~.x[mem == "000"], aes(color = exp, linetype = fcst_exp)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  scale_date() +
  labs(subtitle = "RMSE", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_wrap(~ var, scales = "free_y") +
  theme_minimal()

@@

```{r}
copy(miembros) %>% 
  .[, mean_RMSE := mean(RMSE), by =  .(exp, fcst_exp, date, var)] %>% 
  ggplot(aes(date, RMSE)) +
  geom_line(aes(color = exp, linetype = fcst_exp, 
                grup = interaction(exp, fcst_exp, mem)), alpha = 0.1) +
  geom_line(aes(y = mean_RMSE, color = exp, linetype = fcst_exp)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  scale_date() +
  labs(subtitle = "RMSE", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_wrap(~ var, scales = "free_y") +
  theme_minimal()
```
```{r}

extremos <- miembros %>% 
  .[, .(max_bias = max(BIAS),
        min_bias = min(BIAS)), by = .(var, exp, fcst_exp, date)]

media %>% 
  extremos[., on = .NATURAL] %>% 
  .[exp == "E7"] %>% 
  ggplot(aes(date, BIAS)) +
  geom_ribbon(aes(ymin = min_bias, 
                  ymax = max_bias, fill = exp, group = interaction(exp, fcst_exp)), alpha = 0.2) +
  scale_fill_manual(guide = NULL, values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                                   E6 = "SATWND", E7 = "RAD")) +
  geom_line(aes(color = exp, linetype = fcst_exp)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  scale_date() +
  labs(subtitle = "BIAS", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_wrap(~ var, scales = "free_y") +
  theme_minimal()

media %>% 
  .[, mem := "000"] %>% 
  rbind(., miembros) %>% 
  .[exp == "E7"] %>% 
  ggplot(aes(date, BIAS)) +
  geom_line(data = ~.x[mem != "000"], alpha = 0.1, 
            aes(y = RMSE, color = exp, linetype = fcst_exp, group = interaction(exp, mem, fcst_exp))) +
  geom_line(data = ~.x[mem == "000"], aes(color = exp, linetype = fcst_exp)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  scale_date() +
  labs(subtitle = "BIAS", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_wrap(~ var, scales = "free_y") +
  theme_minimal()

```{r}
cum <- fisica[miembros, on = .NATURAL] %>% 
  separate(fisica, into = c("cumulus", "pbl")) %>% 
  .[, .(BIAS = mean(BIAS)), by = .(exp, fcst_exp, cumulus, var, date)]

media %>% 
  .[, c("exp", "var", "date", "fcst_exp", "BIAS")] %>% 
  .[, ":="(cumulus = "Mean")] %>% 
  rbind(., cum) %>% 
  ggplot(aes(date, BIAS)) +
  geom_line(aes(color = exp, linetype = cumulus)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  geom_hline(yintercept = 0, color = "grey30") +
  scale_linetype_manual(values = c(4, 2, 3, 1)) +
  scale_date() +
  labs(subtitle = "BIAS", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_grid(var~fcst_exp, scales = "free_y") +
  theme_minimal()

cum <- fisica[miembros, on = .NATURAL] %>% 
  separate(fisica, into = c("cumulus", "pbl")) %>% 
  .[, .(RMSE = mean(RMSE)), by = .(exp, fcst_exp, cumulus, var, date)]

media %>% 
  .[, c("exp", "var", "date", "fcst_exp", "RMSE")] %>% 
  .[, ":="(cumulus = "Mean")] %>% 
  rbind(., cum) %>% 
  ggplot(aes(date, RMSE)) +
  geom_line(aes(color = exp, linetype = cumulus)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  # geom_hline(yintercept = 0, color = "grey30") +
  scale_linetype_manual(values = c(4, 2, 3, 1)) +
  scale_date() +
  labs(subtitle = "RMSE", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_grid(var~fcst_exp, scales = "free_y") +
  theme_minimal()
```
```{r}
pbl <- fisica[miembros, on = .NATURAL] %>% 
  separate(fisica, into = c("cumulus", "pbl")) %>% 
  .[, .(BIAS = mean(BIAS)), by = .(exp, fcst_exp, pbl, var, date)]

media %>% 
  .[, c("exp", "var", "date", "fcst_exp", "BIAS")] %>% 
  .[, ":="(pbl = "Mean")] %>% 
  rbind(., pbl) %>% 
  ggplot(aes(date, BIAS)) +
  geom_line(aes(color = exp, linetype = pbl)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  geom_hline(yintercept = 0, color = "grey30") +
  scale_linetype_manual(values = c(1, 2, 3, 4)) +
  scale_date() +
  labs(subtitle = "BIAS", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_grid(var~fcst_exp, scales = "free_y") +
  theme_minimal()

pbl <- fisica[miembros, on = .NATURAL] %>% 
  separate(fisica, into = c("cumulus", "pbl")) %>% 
  .[, .(RMSE = mean(RMSE)), by = .(exp, fcst_exp, pbl, var, date)]

media %>% 
  .[, c("exp", "var", "date", "fcst_exp", "RMSE")] %>% 
  .[, ":="(pbl = "Mean")] %>% 
  rbind(., pbl) %>% 
  ggplot(aes(date, RMSE)) +
  geom_line(aes(color = exp, linetype = pbl)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  # geom_hline(yintercept = 0, color = "grey30") +
  scale_linetype_manual(values = c(1, 2, 3, 4)) +
  scale_date() +
  labs(subtitle = "RMSE", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_grid(var~fcst_exp, scales = "free_y") +
  theme_minimal()
```

@@

### Campos de variables

```{r}
df <- data.frame(
  lead_time = rep(c(6, 12, 18), 4),
  exp = rep(c("E4", "E5", "E6", "E7"), each = 3)
)

files <- purrr::map2_chr(df$lead_time, df$exp, function(l, e) {
  paste0("/home/paola.corrales/datosmunin/EXP/", e, "/FCST/2018112200/NPP/NPP_2018-11-22_00_FC", 
         formatC(l, width = 2, flag = "0"), ".nc")
})

coord <- ReadNetCDF(files[1], vars = c("XLAT", "XLONG"))

var_00 <- purrr::map(files, function(f) {

  meta <- unglue(f, "/home/paola.corrales/datosmunin/EXP/{exp}/FCST/{fcst_exp}/NPP/NPP_{x}_FC{lead}.nc")

  ReadNetCDF(f, vars = c("Q", "T", "V"), subset = list(lev = c(800, 1000))) %>% 
    .[, .(Q = mean(Q),
          T = mean(T),
          V = mean(V)), by = .(lat, lon)] %>% 
    .[, ":="(exp = meta[[1]][["exp"]],
             fcst_exp = meta[[1]][["fcst_exp"]],
             lead_date = ymd_h(meta[[1]][["fcst_exp"]]) + hours(as.numeric(meta[[1]][["lead"]])))]

mcape_00 <- purrr::map(files, function(f) {

  meta <- unglue(f, "/home/paola.corrales/datosmunin/EXP/{exp}/FCST/{fcst_exp}/NPP/NPP_{x}_FC{lead}.nc")

  ReadNetCDF(f, vars = c("MCAPE", "MDBZ")) %>% 
    .[, .(MCAPE = mean(MCAPE, na.rm = TRUE),
          MDBZ = mean(MDBZ, na.rm = TRUE)), by = .(lat, lon)] %>% 
    .[, ":="(exp = meta[[1]][["exp"]],
             fcst_exp = meta[[1]][["fcst_exp"]],
             lead_date = ymd_h(meta[[1]][["fcst_exp"]]) + hours(as.numeric(meta[[1]][["lead"]])))]

}) %>% rbindlist()
```

```{r}
df <- data.frame(
  lead_time = rep(c(0, 6, 12), 4),
  exp = rep(c("E4", "E5", "E6", "E7"), each = 3)
)

files <- purrr::map2_chr(df$lead_time, df$exp, function(l, e) {
  paste0("/home/paola.corrales/datosmunin/EXP/", e, "/FCST/2018112206/NPP/NPP_2018-11-22_06_FC", 
         formatC(l, width = 2, flag = "0"), ".nc")
})

coord <- ReadNetCDF(files[1], vars = c("XLAT", "XLONG"))

var_06 <- purrr::map(files, function(f) {

  meta <- unglue(f, "/home/paola.corrales/datosmunin/EXP/{exp}/FCST/{fcst_exp}/NPP/NPP_{x}_FC{lead}.nc")

  ReadNetCDF(f, vars = c("Q", "T", "V"), subset = list(lev = c(800, 1000))) %>% 
    .[, .(Q = mean(Q),
          T = mean(T),
          V = mean(V)), by = .(lat, lon)] %>% 
    .[, ":="(exp = meta[[1]][["exp"]],
             fcst_exp = meta[[1]][["fcst_exp"]],
             lead_date = ymd_h(meta[[1]][["fcst_exp"]]) + hours(as.numeric(meta[[1]][["lead"]])))]

mcape_06 <- purrr::map(files, function(f) {

  meta <- unglue(f, "/home/paola.corrales/datosmunin/EXP/{exp}/FCST/{fcst_exp}/NPP/NPP_{x}_FC{lead}.nc")

  ReadNetCDF(f, vars = c("MCAPE", "MDBZ")) %>% 
    .[, .(MCAPE = mean(MCAPE, na.rm = TRUE),
          MDBZ = mean(MDBZ, na.rm = TRUE)), by = .(lat, lon)] %>% 
    .[, ":="(exp = meta[[1]][["exp"]],
             fcst_exp = meta[[1]][["fcst_exp"]],
             lead_date = ymd_h(meta[[1]][["fcst_exp"]]) + hours(as.numeric(meta[[1]][["lead"]])))]

}) %>% rbindlist()
```

```{r}
var_00 %>% 
  coord[., on = .NATURAL] %>% 
  .[, c("x", "y") := wrf_project(XLONG, XLAT)] %>% 
  .[, lead_date := factor(lead_date)] %>%

  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = Q, fill = stat(level_d)), proj = norargentina_lambert,
                    breaks = seq(0, 20, 2)) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "BrBG", direction = 1,
                       limits = c(1, 20),
                       guide = guide_colorsteps(#inside = FALSE,
                         barwidth = 25,
                         barheight = 0.8)) +
  geom_mapa() +
  cordillera +
  facet_grid(lead_date ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                          E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

var_06 %>% 
  coord[., on = .NATURAL] %>% 
  .[, c("x", "y") := wrf_project(XLONG, XLAT)] %>% 
  .[, lead_date := factor(lead_date)] %>%

  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = Q, fill = stat(level_d)), proj = norargentina_lambert,
                    breaks = seq(0, 20, 2)) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "BrBG", direction = 1,
                       limits = c(1, 20),
                       guide = guide_colorsteps(#inside = FALSE,
                         barwidth = 25,
                         barheight = 0.8)) +
  geom_mapa() +
  cordillera +
  facet_grid(lead_date ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                          E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```
```{r}
var_00 %>% 
  coord[., on = .NATURAL] %>% 
  .[, c("x", "y") := wrf_project(XLONG, XLAT)] %>% 
  .[, lead_date := factor(lead_date)] %>%

  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = V, fill = stat(level_d)), proj = norargentina_lambert) +
  scale_fill_divergent_discretised(name = NULL,
                                   guide = guide_colorsteps(#inside = FALSE,
                                     barwidth = 25,
                                     barheight = 0.8)) +
  geom_mapa() +
  cordillera +
  facet_grid(lead_date ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                          E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

var_06 %>% 
  coord[., on = .NATURAL] %>% 
  .[, c("x", "y") := wrf_project(XLONG, XLAT)] %>% 
  .[, lead_date := factor(lead_date)] %>%

  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = V, fill = stat(level_d)), proj = norargentina_lambert) +
  scale_fill_divergent_discretised(name = NULL,
                                   guide = guide_colorsteps(#inside = FALSE,
                                     barwidth = 25,
                                     barheight = 0.8)) +
  geom_mapa() +
  cordillera +
  facet_grid(lead_date ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                          E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

```{r}
var_00 %>% 
  coord[., on = .NATURAL] %>% 
  .[, c("x", "y") := wrf_project(XLONG, XLAT)] %>% 
  .[, lead_date := factor(lead_date)] %>%

  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = T - 273.15, fill = stat(level_d)), proj = norargentina_lambert,
                    breaks = seq(0, 40, 5)) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "OrRd", direction = 1,
                       limits = c(1, 40),
                       guide = guide_colorsteps(#inside = FALSE,
                         barwidth = 25,
                         barheight = 0.8)) +
  geom_mapa() +
  cordillera +
  facet_grid(lead_date ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                          E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

var_06 %>% 
  coord[., on = .NATURAL] %>% 
  .[, c("x", "y") := wrf_project(XLONG, XLAT)] %>% 
  .[, lead_date := factor(lead_date)] %>%

  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = T - 273.15, fill = stat(level_d)), proj = norargentina_lambert,
                    breaks = seq(0, 40, 5)) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "OrRd", direction = 1,
                       limits = c(1, 40),
                       guide = guide_colorsteps(#inside = FALSE,
                         barwidth = 25,
                         barheight = 0.8)) +
  geom_mapa() +
  cordillera +
  facet_grid(lead_date ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                          E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```
```{r}
mcape_00 %>% 
  coord[., on = .NATURAL] %>% 
  .[, c("x", "y") := wrf_project(XLONG, XLAT)] %>% 
  .[, lead_date := factor(lead_date)] %>%

  ggplot(aes(x, y)) +
  # geom_point(aes(color = MCAPE)) +
  geom_contour_fill(aes(z = MCAPE, fill = stat(level_d)), proj = norargentina_lambert,
                    breaks = seq(0, 4500, 500)) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "YlOrRd", direction = 1,
                       guide = guide_colorsteps(#inside = FALSE,
                         barwidth = 25,
                         barheight = 0.8)) +
  geom_mapa() +
  cordillera +
  facet_grid(lead_date ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                          E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

mcape_06 %>% 
  coord[., on = .NATURAL] %>% 
  .[, c("x", "y") := wrf_project(XLONG, XLAT)] %>% 
  .[, lead_date := factor(lead_date)] %>%

  ggplot(aes(x, y)) +
  # geom_point(aes(color = MCAPE)) +
  geom_contour_fill(aes(z = MCAPE, fill = stat(level_d)), proj = norargentina_lambert,
                    breaks = seq(0, 4500, 500)) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "YlOrRd", direction = 1,
                       guide = guide_colorsteps(#inside = FALSE,
                         barwidth = 25,
                         barheight = 0.8)) +
  geom_mapa() +
  cordillera +
  facet_grid(lead_date ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                          E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```
```{r}
values <- c(-19.5, -12, -7.5, -3, 1.5, 6, 9, 12, 15, 16.5, 18, 19.5, 21, 
22.5, 24, 25.5, 27, 28.5, 30, 31.5, 33, 34.5, 36, 37.5, 39, 40.5, 
42, 43.5, 45, 46.5, 48, 49.5, 51, 52.5, 54, 55.5, 57, 58.5, 60, 
61.5, 63, 64.5, 66, 69, 76.5)

colours <- c("#3D4170", "#3D4E7C", "#3B5B84", "#3A6695", "#3672A4", "#3188BD", 
"#2F89B9", "#2896C7", "#24A4CF", "#2AB1D6", "#53F336", "#4BE231", 
"#44D12F", "#3FC12B", "#3AAF25", "#32A11F", "#2C881E", "#227216", 
"#EEEF39", "#DEE539", "#D7DA35", "#CED130", "#C4C52B", "#CBAE1F", 
"#D59716", "#DB8116", "#EC0A2E", "#CB001A", "#C20013", "#B10009", 
"#990000", "#C3005D", "#D600A2", "#E901E9", "#CC00CC", "#B100B5", 
"#9800A0", "#FEFFFF", "#DFF5EC", "#C5F1E0", "#B7ECD8", "#A6ECCF", 
"#95E3C5", "#85E0BD")

mcape_00 %>% 
  coord[., on = .NATURAL] %>% 
  .[, c("x", "y") := wrf_project(XLONG, XLAT)] %>% 
  .[, lead_date := factor(lead_date)] %>%

  ggplot(aes(x, y)) +
  # geom_point(aes(color = MCAPE)) +
  geom_contour_fill(aes(z = MDBZ, fill = stat(level)), 
                    proj = norargentina_lambert,
                    breaks = values) +
  scale_fill_manual(values = colours, 
                    drop = FALSE, guide = guide_colorsteps(barwidth = 0.8, 
                                                                         barheight = 30)) +
  geom_mapa() +
  cordillera +
  facet_grid(lead_date ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                          E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

mcape_06 %>% 
  coord[., on = .NATURAL] %>% 
  .[, c("x", "y") := wrf_project(XLONG, XLAT)] %>% 
  .[, lead_date := factor(lead_date)] %>%

  ggplot(aes(x, y)) +
  # geom_point(aes(color = MCAPE)) +
  geom_contour_fill(aes(z = MDBZ, fill = stat(level)), 
                    proj = norargentina_lambert,
                    breaks = values) +
  scale_fill_manual(values = colours, 
                    drop = FALSE, guide = guide_colorsteps(barwidth = 0.8, 
                                                                         barheight = 30)) +
  geom_mapa() +
  cordillera +
  facet_grid(lead_date ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                          E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```
